---
title: "Troy et al data cleaning"
author: "Amanda Mae Woodward"
date: "2023-04-20"
output: html_document
---

# Import Data
```{r}
dat <- read.csv("~/Downloads/troyetal_earlydata.csv", comment.char="#")
```

# Change Column Names
```{r}
colnames(dat)<- c("participantID", "dot", "dobMonth", "dobDay","dobYear", "raceEthnicity", "raceEthnicityDescription", "gender", "genderDescription", "ses","CRA1", "CRA2", "CRA3", "CRA4", "CRA5", "CRA6", "CRA7", "CRA8","HCRA1", "HCRA2", "HCRA3", "HCRA4", "HCRA5", "HCRA6", "DS1", "DS2", "DS3", "DS4", "DS5", "PSS1", "PSS2", "PSS3", "PSS4", "MSES", "MQ1", "MQ2", "MQ3", "MQ4", "MQ5", "MQ6", "MQ7","MQ8", "MQ9", "MQ10", "MQ11", "MQ12", "MQ13","MQ14","MQ15", "BFI1", "BFI2", "BFI3", "BFI4", "BFI5", "BFI6", "BFI7", "BFI8", "BFI9", "BFI10", "BFI11", "BFI12","BFI13","BFI14","BFI15","BFI16", "BFI17", "BFI18","BFI19", "BFI20", "BFI21","BFI22", "BFI23", "BFI24", "BFI25", "BFI26", "BFI27", "BFI28", "BFI29", "BFI30", "BFI31", "BFI32", "BFI33", "BFI34","BFI35","BFI36","BFI37","BFI38", "BFI39", "BFI40","BFI41", "BFI42", "BFI43","BFI44")
```

# To Do: double check race/ethnicity column and gender column to make sure all info is in one column 


# Getting Scale Scores:

# CRA: 8 eight items
1 = "Strongly disagree"
2 = "disagree"
3 = "somewhat disagree" 
4 = "neutral"
5 = "somewhat agree"
6 = "agree" 
7 = "strongly agree"
```{r}
library(car)
dat$CRA1<- recode(dat$CRA1, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA2<- recode(dat$CRA2, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA3<- recode(dat$CRA3, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA4<- recode(dat$CRA4, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA5<- recode(dat$CRA5, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA6<- recode(dat$CRA6, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA7<- recode(dat$CRA7, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
dat$CRA8<- recode(dat$CRA8, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neutral" = 4; "Somewhat agree" =5; "Agree" = 6; "Strongly agree" = 7')
```

# PSS: 4 items
- 1-4

1 = "Never"
2 = "Almost Never"
3 = "Sometimes"
4 = "Fairly Often"
5 = "Very Often"

```{r}
dat$PSS1<- recode(dat$PSS1, recodes = '"Never" = 1; "Almost Never" = 2; "Sometimes" = 3; "Fairly Often" = 4; "Very Often" = 5')
dat$PSS2<- recode(dat$PSS2, recodes = '"Never" = 5; "Almost Never" = 4; "Sometimes" = 3; "Fairly Often" = 2; "Very Often" = 1')
dat$PSS3<- recode(dat$PSS3, recodes = '"Never" = 5; "Almost Never" = 4; "Sometimes" = 3; "Fairly Often" = 2; "Very Often" = 1')
dat$PSS4<- recode(dat$PSS4, recodes = '"Never" = 1; "Almost Never" = 2; "Sometimes" = 3; "Fairly Often" = 4; "Very Often" = 5')
```

# Depressive Symptoms: 5 items
- 1-4

1 = "Rarely or none of the time (less than 1 day)"
2 = "Some or a little of the time (1-2 days)"
3 = "Occasionally or moderate amount of time (3-4 days)"
4 = "Most or all of the time (5-7 days)"

```{r}
dat$DS1<- recode(dat$DS1, recodes = '"Rarely or none of the time (less than 1 day)" = 1; "Some or a little of the time (1-2 days)" = 2; "Occasionally or moderate amount of time (3-4 days)" = 3; "Most or all of the time (5-7 days)" = 4')
dat$DS2<- recode(dat$DS2, recodes = '"Rarely or none of the time (less than 1 day)" = 1; "Some or a little of the time (1-2 days)" = 2; "Occasionally or moderate amount of time (3-4 days)" = 3; "Most or all of the time (5-7 days)" = 4')
dat$DS3<- recode(dat$DS3, recodes = '"Rarely or none of the time (less than 1 day)" = 1; "Some or a little of the time (1-2 days)" = 2; "Occasionally or moderate amount of time (3-4 days)" = 3; "Most or all of the time (5-7 days)" = 4')
dat$DS4<- recode(dat$DS4, recodes = '"Rarely or none of the time (less than 1 day)" = 1; "Some or a little of the time (1-2 days)" = 2; "Occasionally or moderate amount of time (3-4 days)" = 3; "Most or all of the time (5-7 days)" = 4')
dat$DS5<- recode(dat$DS5, recodes = '"Rarely or none of the time (less than 1 day)" = 1; "Some or a little of the time (1-2 days)" = 2; "Occasionally or moderate amount of time (3-4 days)" = 3; "Most or all of the time (5-7 days)" = 4')
```


HCRA
Strongly Disagree  = 1
Disagree = 2
Somewhat disagree = 3
Neither agree or disagree = 4
Somewhat agree =5
Agree = 6
Strongly Agree =7
```{r}
dat$HCRA1 <- recode(dat$HCRA1, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7')
dat$HCRA2 <- recode(dat$HCRA2, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7')
dat$HCRA3 <- recode(dat$HCRA3, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7')
dat$HCRA4 <- recode(dat$HCRA4, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7')
dat$HCRA5 <- recode(dat$HCRA5, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7')
dat$HCRA6 <- recode(dat$HCRA6, recodes = '"Strongly disagree" = 1; "Disagree" = 2; "Somewhat disagree" = 3; "Neither agree nor disagree" = 4; "Somewhat agree" = 5; "Agree" = 6; "Strongly agree" = 7’)
```

# Mindfulness Questionnaire
almost never =1
very infrequently = 2
somewhat infrequently = 3
somewhat frequently = 4
very frequently = 5
almost always =6

```{r}
dat$MQ1 <- recode(dat$MQ1, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ2 <- recode(dat$MQ2, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ3 <- recode(dat$MQ3, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ4 <- recode(dat$MQ4, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ5 <- recode(dat$MQ5, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ6 <- recode(dat$MQ6, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ7 <- recode(dat$MQ7, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ8 <- recode(dat$MQ8, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ9 <- recode(dat$MQ9, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ10 <- recode(dat$MQ10, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ11 <- recode(dat$MQ11, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ12 <- recode(dat$MQ12, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ13 <- recode(dat$MQ13, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ14 <- recode(dat$MQ14, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
dat$MQ15 <- recode(dat$MQ15, recodes = '"Almost Never" = 1; "Very Infrequently" = 2; "Somewhat Infrequently" = 3; "Somewhat Frequently" = 4; "Very Frequently" = 5; "Almost Always" = 6')
```

# BFI 
#Extraversion normal subscale
```{r}
dat$BFI1 <- recode(dat$BFI1, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI11 <- recode(dat$BFI11, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI16 <- recode(dat$BFI16, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI26 <- recode(dat$BFI26, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI36 <- recode(dat$BFI36, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
```
#extraversion inverse subscale
5= "disagree a lot"
4= "disagree"
3= "neutral"
2="agree"
1="agree a lot"
```{r}
dat$BFI6 <- recode(dat$BFI6, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI21 <- recode(dat$BFI21, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI31<- recode(dat$BFI31, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
```
#Agreeableness normal subscale
```{r}
dat$BFI7 <- recode(dat$BFI7, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI17 <- recode(dat$BFI17, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI22 <- recode(dat$BFI22, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI32 <- recode(dat$BFI32, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI42 <- recode(dat$BFI42, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
```
#Agreeableness inverse subscale
```{r}
dat$BFI2 <- recode(dat$BFI2, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI12 <- recode(dat$BFI12, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI27 <- recode(dat$BFI27, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI37 <- recode(dat$BFI37, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
```
#Conscientiousness normal Subscale
```{r}
dat$BFI3 <- recode(dat$BFI3, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI13 <- recode(dat$BFI13, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI28 <- recode(dat$BFI28, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI33 <- recode(dat$BFI33, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI38 <- recode(dat$BFI38, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
```
#Conscientiousness inverse Subscale
```{r}
dat$BFI8 <- recode(dat$BFI8, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI18 <- recode(dat$BFI18, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI23 <- recode(dat$BFI23, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI43 <- recode(dat$BFI43, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
```

#Neuroticism normal subscale
```{r}
dat$BFI4 <- recode(dat$BFI4, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI14 <- recode(dat$BFI14, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI19 <- recode(dat$BFI19, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI29 <- recode(dat$BFI29, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI39 <- recode(dat$BFI39, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
```

#Neuroticism inverse subscale
```{r}
dat$BFI9 <- recode(dat$BFI9, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI24 <- recode(dat$BFI24, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI34 <- recode(dat$BFI34, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
```

#Openess normal subscale
```{r}
dat$BFI5 <- recode(dat$BFI5, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI10 <- recode(dat$BFI10, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI15 <- recode(dat$BFI15, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI20 <- recode(dat$BFI20, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI25 <- recode(dat$BFI25, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI30 <- recode(dat$BFI30, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI40 <- recode(dat$BFI40, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
dat$BFI44 <- recode(dat$BFI44, recodes = '"Disagree a lot" = 1; "Disagree" = 2; "Neutral" = 3; "Agree" = 4; "Agree a lot" = 5')
```

#Openess inverse subscale
```{r}
dat$BFI35 <- recode(dat$BFI35, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
dat$BFI41 <- recode(dat$BFI41, recodes = '"Disagree a lot" = 5; "Disagree" = 4; "Neutral" = 3; "Agree" = 2; "Agree a lot" = 1')
```
